---
title: "p8105_hw1_cw3747"
author: "chuhan wang_cw3747"
date: "2025-09-14"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1
## Description of the dataset 
First, we use the `early_january_weather` dataset from the `moderndive` package and start by checking the variable names, structure, and basic summary statistics.
```{r}
library(moderndive)
data("early_january_weather")
names(early_january_weather)
head(early_january_weather)
str(early_january_weather)

summary(early_january_weather$temp)
summary(early_january_weather$humid)
summary(early_january_weather$dewp)
table(early_january_weather$origin)

nrow(early_january_weather)
ncol(early_january_weather)
```
The dataset early_january_weather contains 358 observations and 15 variables. The variables include identifiers of date and time (year, month, day, hour, time_hour), weather measurements (temperature temp, dew point dewp, humid, wind direction, wind speed, wind gust, pressure, precipitation, visibility), and the station of origin.

The mean temperature during this period collected at Newark Airport is about 39.6째F (approximately ranging from 24째F to 58째F). 

## Figure
We use the 'ggplot' to create a scatterplot of temperature over time, with points colored by humidity.  
```{r}
library(ggplot2)
ggplot(early_january_weather, aes(x = time_hour,
                                  y = temp,
                                  color = humid) ) + 
  geom_point() + 
  labs(title = "Early Temperature in January",
       x = "Time(hour)",
       y = "Temperature(째F)",
       color = "Humdity(%)") + 
theme_minimal()
ggsave("figure of early temp in Jun.png", width = 7, height = 4)
```

# Problem 2
## Data Frame
We first create a dataframe with four different types of variables: numeric, logical, character, and factor.
```{r}
x_numeric = rnorm(10)
x_logical = x_numeric > 0
x_char = letters[1:10]
x_factor = factor(rep(c("low", "medium", "high"), length.out = 10))

df = data.frame(
  x_numeric = x_numeric,
  x_logical = x_logical,
  x_char = x_char,
  x_factor = x_factor
)
```

## Mean
Before calculating, we need to pull the variable out of the dataframe.
```{r, error=TRUE}
library(tidyverse)
df %>% pull(x_numeric) %>% mean()
df %>% pull(x_logical) %>% mean()
df %>% pull(x_char) %>% mean()
df %>% pull(x_factor) %>% mean()
```
We can see because of some non-numeric variables, the mean cannot be calculated.
```{r}
as.numeric(x_char)
as.numeric(x_factor)
```
As a result, the mean of numeric variables can be calculated directly. And the mean of logical variables depends on the proportion of TRUE values, because R literally treats TRUE as 1 and FALSE as 0. At last, the mean of character and factors do not have meaningful interpretation due to these data types are categorical. Even if they are coerced into numeric form, the results do not mean anything.